% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{times}
%\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\usepackage{geometry}
\geometry{lmargin =25mm, rmargin = 35mm, tmargin=25mm, bmargin=20mm}

\begin{document} 

\name{VIJAYALEKSHMI KESAVAN\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\textbf{Email:} vijayalekshmikesavan@gmail.com}
\address{\textbf{Mobile:} +919480655011}
                                  
\begin{resume}

\section{WORK EXPERIENCE}
\textbf{\\Engineer, HealthcareMagic (August 2014 - Present)}

\begin{itemize}

\item Manage the entire frontend and backend stack of healthcaremagic.com being an individual contributor. 
\item Major Contributons: 
\begin{itemize}
\item Designed and implemented Restful APIs to extend our health services to third parties, a kiosk service for Rajastan government and a portal for middle east doctors to name a couple.
\item Worked with several internal teams (operations, content management, doctors etc.) and external clients to build systems to improve operations.
\end {itemize}
\end {itemize}
\textbf{Senior Engineer, @walmartlabs (April 2012 - February 2014)}

\begin{itemize}

\item {Display Advertisement Technology:} Worked on building a Real Time Bidding Ad platform in partnership with external DSPs which was tailored for re-targeting users.
\item {Keyword Intelligence for SEO and SEM:} Worked on mining relevant keywords and recommending keywords for walmart.com items. Used Google Adwords API and internal Muppet (Fast processor for streaming data) application to process keywords.
\end {itemize}
\textbf{Software Development Engineer, Amazon.com (July 2009 - April 2012)}

\begin{itemize}

\item {Tiered Storage for Ordering:} Managed various storage frameworks for checkout applications. Worked on order data migration from Mysql to Amazon S3 and Shopping Cart deprecation from Dynamo.
\item {Data Warehousing and Business Intelligence:} Worked for Amazon's core DW/BI Team taking responsibilities including Data Modeling, SQL Development and Project Management, while handling massive data volumes. 
\end {itemize}

\section{TECHNICAL INTERESTS}  
Algorithms, Machine Learning, Data Science, Distributed Systems

\section{TECHNOLOGIES WORKED ON}
\textbf{Programming Languages:} Java, C, JavaScript, Python, SQL\\
\textbf{Databases:} MySQL, Hive, Redis\\
\textbf{Development Tools:} git, maven, ant, jenkins\\
\textbf{Web Technologies:} HTML, CSS, jQuery, Bootstrap

\section{EDUCATIONAL QUALIFICATIONS}				
\textbf{\\}
\begin{tabular}{| p{4.7cm}|p{5.5cm}|p{1.6cm}|p{1.7cm}|}
\hline \textbf{Degree and Branch} & \textbf{University} & \textbf{Duration} & \textbf{\% / CGPA} \\ 
\hline MTech, Computer Science and  Engineering & Indian Institute of Technology, Madras & 2007-2009 & 8.97/10 \\ 
\hline BTech, Computer Science and  Engineering & TKM College of Engg., Kollam / Kerala University & 2003-2007 & 8.30/10 \\ 
\hline Higher Secondary Education(XII) & Board of Higher Secondary Examination, Kerala & 2001-2003 & 92.83\% \\ 

\hline 
\end{tabular} 

\section{ACADEMIC PROJECTS}
\begin{itemize}

\item {Active Machine Learning for State Mapping (2008-2009)}

Worked on an emerging Machine Learning research area called Active Learning, which is a technique used in Supervised learning algorithms to minimize the cost involved in learning a task. As part of the project, we proposed and implemented an Active learning algorithm to transfer the learning from a Robotic Agent to another, first one being a Robot that was already trained in similar environments, by mapping states in a Transfer learning model.

\item {Air Conditioner Maintenance and Complaint Tracking Software for IIT Madras.(2007)}

Developed a web based application to track the complaints to AC Maintenance Dept.. This was done in PHP-MySQL-Apache platform and was deployed in IIT Madras Intranet.

\item {Computational Geometry based Path planning and Visibility polygon detection (2006-2007)}

Worked on two research problems in Computational Geometry with applications to Robotics. Problems: (1) Finding the shortest path for a point robot in a room with polygonal obstacles. (2) Finding the visibility polygon for a point light source in a room with polygonal obstacles. Developed and implemented two novel algorithms to accomplish the above tasks with promising results.

\end{itemize}
  
\section{RELEVANT COURSES DONE}

\textbf{Graduate level:} 
Advanced Data Stuctures and Algorithms, 
Topics in Approximation and Randomized Algorithms and Zero Knowledge Protocols, 
Reinforcement Learning, 
Data Mining, 
Advanced Computer Networks, 
Real-time Computing and Communication, 
Advanced Computer Architecture, 
Software Engineering: Theory and Practice, 
Advanced Mathematical Concepts in Computer Science.

\textbf{Undergraduate Level:}
Computational Geometry, 
Algorithm Analysis and Design, 
Distributed Systems, 
Cryptography and Network Security, 
Wireless Networks, 
High Performance Computer Systems

\section{ACADEMIC ACHIEVEMENTS}          
\begin{itemize}
\item Outstanding Teaching Assistant award for the year 2009 in IIT Madras.
\item All India Rank 101 in GATE 2007 (for CSE) Examination
\item TCS Best Student Award during under-graduate studies in TKM CE, Kollam in 2007
\item College Topper and University 4th Rank holder for BTech
\item School and District level topper for Higher Secondary Examination

\end{itemize}

\section{OTHER INTERESTS}

\begin{itemize}
\item Philosophy, Psychology, Cognitive Sciences
\item Music, Photography, Running, Trekking 

\end{itemize} 
\end{resume}
\end{document}
