% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{times}
%\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\usepackage{geometry}
\geometry{lmargin =25mm, rmargin = 30mm, tmargin=25mm, bmargin=20mm}

\begin{document} 

\name{VIJAYALEKSHMI KESAVAN\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\textbf{Email:} vijayalekshmikesavan@gmail.com}
\address{\textbf{Mobile:} +919492529285}
                                  
\begin{resume}

\section{EDUCATIONAL QUALIFICATIONS}				
\textbf{\\}
\begin{tabular}{| p{4.7cm}|p{5.5cm}|p{1.6cm}|p{1.7cm}|}
\hline \textbf{Degree and Branch} & \textbf{Institute / University} & \textbf{Duration} & \textbf{\% / CGPA} \\ 
\hline MTech, Computer Science and  Engineering & Indian Institute of Technology, Madras & 2007-2009 & 8.97/10 \\ 
\hline BTech, Computer Science and  Engineering & TKM College of Engg., Kollam / Kerala University & 2003-2007 & 8.30/10 \\ 
\hline Higher Secondary Education(XII) & SCSHSS, Thiruvalla / Board of Higher Secondary Examination, Kerala & 2001-2003 & 92.83\% \\ 
\hline Secondary Education(X) & SCSHSS, Thiruvalla / Board of Secondary Examination, Kerala & 2001 & 85.33\% \\ 
\hline 
\end{tabular} 

\section{WORK EXPERIENCE}

\textbf{\\Software Development Engineer, Amazon.com (July 2009 - Present)}

\begin{itemize}

\item Individual Contributer in Datawarehousing and Business Intelligence Team. 
\item As an IC, worked on Projects in all the phases starting from Requirement Analysis through Design and Data Modelling to Delivery and Support.
\item Majorly technologies used: Oracle 11g, Teradata, SQL, PL/SQL, Datanet(Home-grown ETL Tool), Perl etc. 
\end {itemize}  

\section{ACADEMIC PROJECTS UNDERTAKEN}
\begin{itemize}
\item {Computational Geometry based Path planning and Visibility polygon detection (2006-2007)}

As part of the Undergraduate programme, did research on two problems in Computational Geometry which had got application in Robotics. Problems: (1) Finding the shortest path for a point robot in a room with polygonal obstacles. (2) Finding the visibility polygon for a point light source in a room with polygonal obstacles. We (a team of 3 members) framed and implemented two novel algorithms to accomplish the above tasks which gave promising results.

\item {Air Conditioner Maintenance and Complaint Tracking Software for IIT Madras.(2007)}

Developed a web based application in PHP-MySQL-Apache platform and deployed in IIT Madras Intranet as part of the Software Engineering Course in during graduation.

\item {Active Machine Learning and its applications in Transfer Learning (2008-2009)}

Carried out an extensive Literature Survey and research in Active Learning(a technique widely used by supervised learning algorithms) and developed an active learning algorithm to transfer the learning from one Robotic Agent to another, first one being a Robot that was already trained in similar environments. 

\end{itemize}
	
\section{TECHNOLOGIES WORKED ON}
\textbf{Programming languages:} C, C++, SQL, PL/SQL, Perl, Python\\
\textbf{Databases:} Oracle, Teradata, MySQL\\
\textbf{Tools:} Matlab, Weka, libsvm, RL-Glue, ns2-Network Simulator, Latex, Datanet(ETL tool)\\
\textbf{Programming Tools:} vim, gdb, make, RCS, Eclipse

\section{INTERESTED SUBJECT AREAS}  
Algorithms, Machine Learning, Distributed Systems.
  
\section{RELEVANT COURSES DONE}

\textbf{Graduate level:} 
Advanced Data Stuctures and Algorithms, 
Topics in Approximation and Randomized Algorithms and Zero Knowledge Protocols, 
Reinforcement Learning, 
Data Mining, 
Advanced Computer Networks, `
Real-time Computing and Communication, 
Advanced Computer Architecture, 
Software Engineering: Theory and Practice, 
Advanced Mathematical Concepts in Computer Science.

\textbf{Undergraduate Level:}
Computational Geometry, 
Algorithm Analysis and Design, 
Distributed Systems, 
Cryptography and Network Security, 
Wireless Networks, 
High Performance Computer Systems

\section{ACADEMIC ACHIEVEMENTS}          
\begin{itemize}
\item Outstanding TA (Teaching Assistant) award for odd semester, 2009 in IIT Madras.
\item All India Rank 101 in GATE 2007 (for CSE) Examination
\item TCS Best Student Award during under-graduate studies in TKM CE, Kollam in 2007
\item College Topper and University 4th Rank holder for BTech
\item School and District level topper for Higher Secondary Examination

\end{itemize}

\section{OTHER ACIVITIES AND INTERESTS}

\begin{itemize}
\item Various Programming and Data Mining Competitions
\item History, Philosophy, Psychology and related topics
\item Photography
\item Walking
\item Music, Movies and Theatre Arts

\end{itemize} 
\end{resume}
\end{document}